An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps

### 2019-01-18 algorithm_radix.Rmd
Expanded introduction

---
title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
author:
  - name: Stephanie Kobakian
    url: https://github.com/srkobakian
    affiliation: nswmania University of Technology
date: "`r Sys.Date()`"
output: radix::radix_article
---

@@

Spatial distrbutions have utilised alternative representations of geography for many years. In modern times with the ease of interactivity and animation, alternative representations have been popularised by online news sites. Applications are iincreasingly widespread, especially in the area of disease mapping.

@@

This provides an opportunity for a new class of

@@

```{r}
width <- 30 # arbitrary angle width
```

@@

## Use the create_centroids function to find polygon centroids:
centroids <- create_centroids(shp_sf = nsw_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
```

>>>>

---
title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
author:
  - name: Stephanie Kobakian
    url: https://github.com/srkobakian
    affiliation: Queensland University of Technology
date: "`r Sys.Date()`"
output: radix::radix_article
---

@@

Spatial distrbutions have utilised alternative representations of geography for many years. In modern times with the ease of interactivity and animation, alternative representations have been popularised by online news sites, with a focus on public consumption. Applications are increasingly widespread, especially in the area of disease mapping, election results and .

@@

@@

```{r}
width <- 15 # arbitrary angle width
```

@@

## Use the create_centroids function to find polygon centroids:
centroids <- create_centroids(shp_sf = nsw_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)

fort_nsw <- fortify_sfc(nsw_lga, projstring = projstring)
```
